\documentclass[8pt]{resumeclass}
%\documentclass[9pt]{backup_resumeclass}

\begin{document}

%-----------------------------------------------------------------------------------------------------------
%	NAME AND CONTACT INFO
%-----------------------------------------------------------------------------------------------------------

\begin{minipage}[t]{0.65\textwidth}							% Use 65% of the page for name
	\vspace{-\baselineskip}								% Vertically align minipage

	\colorbox{black}{\huge\textcolor{white}{\textbf{\MakeUppercase{Eric}}}}

	\colorbox{black}{\huge\textcolor{white}{\textbf{\MakeUppercase{Kearney}}}}
	
	\vspace{6pt}

	{\huge Software Engineer}
\end{minipage}
\begin{minipage}[t]{0.35\textwidth}							% Use 35% of the page for contact information
	\vspace{-\baselineskip}
	\vspace{15pt}
	\colorbox{black}{\textcolor{white}{\textbf{\MakeUppercase{Contact}}}}\\
	{\textbf{303 596 5371}}\\
	{\href{mailto:erickearney@protonmail.com}{\textbf{erickearney@protonmail.com}}}\\
	{\href{https://github.com/erkearney}{\textbf{github.com/erkearney}}}\\
	{\href{https://aeryck.com}{\textbf{aeryck.com}}}
\end{minipage}

\vspace{3pt}

%-----------------------------------------------------------------------------------------------------------
%	Experience
%-----------------------------------------------------------------------------------------------------------

\resumesect{Experience}
\colorbox{black}{\small\textcolor{white}{\textbf{\MakeUppercase{Raytheon Technologies -- Aurora, CO}}}}
\vspace{6pt}

\begin{entrylist}
	\entry
		{Nov. 2021 -- Present}
		{Joint Polar Satelite System}
		{Software Engineer}
		{Supported after release, responsibilites included bug-fixing, code cleanup, and reconfiguring various subsystems to dynamically meet customer needs.}
	\entry
		{Mar. 2021 -- Nov. 2021}
		{HP Replacement of IBM Products}
		{Scurm Master}
		{Served as a Scrum master to the completion of a server infrastructure migration project. Responsibilites included running daily standups, flowing progress up the proper lines of communication, and quickly eliminating blockers for developers.}
	\entry
		{Aug. 2019 -- Mar. 2021}
		{GPS-OCX}
		{Software Engineer / Discrepency Report Lead}
		{Served as a test engineer and debugger. Processed reported issues and discrepencies into work orders. Identified high priority issues and helped determine which engineer(s) would be best suited to each task.}
\end{entrylist}

%-----------------------------------------------------------------------------------------------------------
%	PROJECTS
%-----------------------------------------------------------------------------------------------------------

\resumesect{Highlighted Projects}

\begin{entrylist}
	\entry
		{Jan. 2022 - May 2022}
		{Graduate-level Big Data Term Project}
		{Data Science}
		{\vspace{-3mm}\begin{itemize}[noitemsep,nolistsep]
			\small
			\item Worked with a small team to create a model that predicts IMDB ratings, Rotten Tomatoes user and critic score, and Box Office performance of movies.
			\item Written in Python using PyTorch and deployed on Apache Spark.
			\item Wrote web scrapers to harvest raw data from sources that did not provide an API.
		\end{itemize}}
	\entry
		{Jan. 2019 - May 2019}
		{Undergraduate-level Digital Image Processing}
		{Computer Vision}
		{{\vspace{-3mm}\begin{itemize}[noitemsep,nolistsep]
			\small
			\item Implemented face detection, edge detection/sharpening, noise/lighting correciton, facial recognition, and visual saliency calculation across images.
			\item Wrote a simple model to analyze driving footage and automatically detect crashes in said footage.
		\end{itemize}}}
	\entry
		{Jan. 2018 - May 2018}
		{Undergraduate-level Email Analysis}
		{Natural Language Processing}
		{{\vspace{-3mm}\begin{itemize}[noitemsep,nolistsep]
			\small
		\item Used scikit learn, Natual Language Toolkit, and a dataset of around half a million emails sent by senior management at Enron to write a program that takes an email as an input and predicts which manager wrote that email, with an accuracy of about 80\%.
		\end{itemize}}}
\end{entrylist}

%-----------------------------------------------------------------------------------------------------------
%	Education
%-----------------------------------------------------------------------------------------------------------

\resumesect{Education}

\begin{entrylist}
	\entry
		{Jan. 2022 -- Dec. 2023\\ (expected)}
		{Master's in Computer Science}
		{Colorado State University}
		{Currently enrolled in a Master's program in Computer Science with a focus in big data and machine learning.}
	\entry
		{Jan. 2017 -- May 2019}
		{Bachelor's in Computer Science}
		{Metropolitan State University of Denver}
		{{\vspace{-5mm}\begin{itemize}[noitemsep,nolistsep]
			\item GPA: 4.0
			\item Graduated Summa Cum Laude and with Highest Honors
			\item Awarded by the department of Mathematics and Computer Science for "Exceptional accomplishments in Computer Science"
		\end{itemize}}}
\end{entrylist}

%-----------------------------------------------------------------------------------------------------------
%	MISCELLANEOUS
%-----------------------------------------------------------------------------------------------------------

\vspace{6pt}
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip}

	\resumesect{\small Languages}
	\boldwithparens{Python}{PyTorch, NumPy, Pandas, Flask, OpenCV}
	\boldwithparens{Java}{Gradle, JSF, JUnit}
	\boldwithparens{SQL}{PostgresQL, MySQL, SQLite}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip}

	\resumesect{\small Development Tools}
	\boldwithparens{Continuous Integration}{Git, Jenkins}
	\boldwithparens{Linux Administration}{Fedora/Red Hat}
	\textbf{Jira, Confluence, Docker}\\
\end{minipage}

\end{document}
