\documentclass[12pt]{resumeclass}

\begin{document}

\vspace{12pt}
%-----------------------------------------------------------------------------------------------------------
%	NAME AND CONTACT INFO
%-----------------------------------------------------------------------------------------------------------
\centerline{\textbf{\LARGE{Eric Kearney}}}
\vspace{2pt}
\centerline{\textbf{\large{Software Engineer}}}
\vspace{2pt}
\centerline{303 596 5371 $|$
\href{mailto:erickearney@protonmail.com}{erickearney@protonmail.com} $|$ Current
TS/SSBI clearance}
\vspace{2pt}
\rule{\textwidth}{0.4pt}
\vspace{0.5pt}

%-----------------------------------------------------------------------------------------------------------
%	Education
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Education}
    {\textbf{Colorado State University} \hfill \normalsize{Jan. 2022 - Dec. 2025
    (expected)}\\
    \small{\textbf{Master's of Science - Computer Science}\\
    Focus in Machine Learning and Data Science. GPA: 3.778}

    \vspace{6pt}
    \textbf{Metropolitan State University of Denver} \hfill \normalsize{Jan.
    2017 - May 2019}\\
    \small{\textbf{Bachelor's of Science - Computer Science}\\
    Awarded by the department of Computer Science for "Exceptional
    accomplishments in Computer Science". GPA: 4.00}}

\vspace{18pt}
%-----------------------------------------------------------------------------------------------------------
%	Experience
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Experience}
    {\textbf{\large{Raytheon Technologies -- Aurora, CO}} \hfill \textbf{Aug. 2019 - Present}


    \vspace{3pt}
    \experiencesect
	{Software Engineer II}
	{Joint Polar Satellite System}
	{Nov. 2021 - Jan. 2023}
	{\begin{itemize}[noitemsep,nolistsep]
	    \item Supported the File Transfer System by correcting bugs discovered by other engineers and end-users
	    \item Successfully completed build close out while working on
	    multiple parallel projects, and consistently pulled to provide
	    operational support, resolve high-priority defects, and respond to
	    direct client inquiries and requests
	    \item Developed new features to streamline and simplify development
	    process
	    \item Reduced time to complete of background processes from days down to
	    a couple hours
	\end{itemize}}


    \vspace{3pt}
    \experiencesect
	{Scrum Master}
	{HP Replacement of IBM Products}
	{Mar. 2021 - Nov. 2021}
	{\begin{itemize}[noitemsep,nolistsep]
	    \item Organized small team during the process of migrating server
	    infrastructure
	    \item Ran quick and effective daily standups
	    \item Efficiently eliminated blockers
	    \item Transformed previously lagging team into top performer
	\end{itemize}}


    \vspace{3pt}
    \experiencesect
	{Test Engineer}
	{GPS-OCX}
	{Aug. 2019 - Mar. 2021}
	{\begin{itemize}[noitemsep,nolistsep]
	    \item Wrote clean, low overhead unit and functional tests
	    \item Revived dead scripts, and updated them to IEEE standards at
	    the client's request, said scripts served as the basis for future
	    client deliverables
	    \item Processed reported issues and discrepancies into work orders
	    \item Identified high priority issues and worked closely with leadership to help determine which engineer(s) would be best suited to individual tasks
	\end{itemize}}}


\vspace{18pt}
%-----------------------------------------------------------------------------------------------------------
%	Projects
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Projects}
    {\href{https://github.com/erkearney/investing-subreddit-analysis}{\textbf{Investing
    Subreddit Analysis}}
    \begin{itemize}[noitemsep,nolistsep]
	\item Created script to analyze the sentiment of thousands of comments
	from \href{reddit.com}{reddit.com} to determine a subreddit's attitude towards a given
	company
	\item Assembled portfolios for each subreddit based on their sentiment,
	and analyzed and compared the performance of these portfolios to
	determine a 'winner'
    \end{itemize}

    \vspace{3pt}
    \textbf{Email De-anonymizer}
    {\begin{itemize}[noitemsep,nolistsep]
	\item Used a publically available dataset of emails sent by upper management at Enron to train a model that reads an email and predicts which manager wrote that email
	\item Accuracy of about 80\%
    \end{itemize}}}


\vspace{18pt}
%-----------------------------------------------------------------------------------------------------------
%	Skills
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Skills}
    {\setstretch{1.25}
    \textbf{Python}: NumPy, pandas, PyTorch, OpenCV, Flask, Django, PySpark,
    pylint, pytest, Jupyer\\
    \textbf{Java:} Gradle, Groovy, JUnit, Cucumber\\
    \textbf{JavaScript:} React\\
    \textbf{Scripting:} Bash, Powershell\\
    \textbf{Big Data Tools:} SQL (PostgreSQL, MySQL, SQLite,
    SQLalchemy), Spark, Hadoop\\
    \textbf{Development Tools:} Linux (Debain/Ubuntu, Fedora/Red Hat), Git, AWS,
    Jenkins, Jira, Confluence\\
    \textbf{Current TS/SSBI clearance}}

\end{document}
