\documentclass[8pt]{resumeclass}

\begin{document}

%-----------------------------------------------------------------------------------------------------------
%	NAME AND CONTACT INFO
%-----------------------------------------------------------------------------------------------------------
\centerline{\textbf{\LARGE{Eric Kearney}}}
\vspace{2pt}
\centerline{303 596 5371 $|$
\href{mailto:erickearney@protonmail.com}{erickearney@protonmail.com} $|$
\href{https://github.com/erkearney}{github.com/erkearney} $|$ Current Top Secret
security clearance}
\vspace{2pt}
\rule{\textwidth}{0.4pt}
\vspace{0.5pt}

%-----------------------------------------------------------------------------------------------------------
%	Summary
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Summary}
    {Results-driven software engineer with 3.5 years of professional experience
    in software development, testing, and project management. Demonstrated
    ability to design, develop, and deploy complex software systems for clients
    in aerospace and defense. Strong problem-solving skills and experience in
    using machine learning and big data tools to derive insights from complex
    datasets.}
\vspace{8pt}

%-----------------------------------------------------------------------------------------------------------
%	Experience
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Experience}
    {\textbf{\large{Raytheon Technologies -- Aurora, CO}} \hfill \textbf{Aug. 2019 - Present}
    \vspace{3pt}\\
    \experiencesect
	{Software Engineer II}
	{Joint Polar Satellite System}
	{Nov. 2021 - Jan. 2023}
	{\begin{itemize}[noitemsep,nolistsep]
	    \item Identified and corrected critical bugs in File Transfer
	    System, improving system reliability 
	    \item Developed and implemented scalable data pipeline by balancing
	    load across multiple servers in a muli-threaded solution; reduced
	    the time-to-complete of mission critical jobs from days to hours
	    \item Successfully completed build close out while working on
	    multiple parallel projects, and consistently pulled to provide
	    operational support, resolve high-priority defects, and respond to
	    direct client inquiries and requests
	\end{itemize}}
    \vspace{3pt}
    \experiencesect
	{Scrum Master}
	{HP Replacement of IBM Products}
	{Mar. 2021 - Nov. 2021}
	{\begin{itemize}[noitemsep,nolistsep]
	    \item Served as Scrum Master to fill void created by staffing
	    shortage, lead team of six during the process of migrating server
	    infrastructure
	    \item Transformed previously lagging team into top performer
	\end{itemize}}
    \vspace{3pt}
    \experiencesect
	{Test Engineer}
	{GPS-OCX}
	{Aug. 2019 - Mar. 2021}
	{\begin{itemize}[noitemsep,nolistsep]
	    \item Wrote clean and concise unit and functional tests and achieved
	    broad and deep test coverage of codebase
	    \item Revived dead scripts, and updated them to IEEE standards at
	    the client's request, said scripts served as the basis for future
	    client deliverables
	    \item Maintained nightly test pipeline to ensure high quality and
	    error-free code
	\end{itemize}}}
\vspace{8pt}
%-----------------------------------------------------------------------------------------------------------
%	Projects
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Projects}
    {\href{https://github.com/erkearney/investing-subreddit-analysis}{\textbf{Investing
    Subreddit Analysis}}
    \begin{itemize}[noitemsep,nolistsep]
	\item Created script to analyze the sentiment of thousands of comments
	from \href{reddit.com}{reddit.com} to determine a subreddit's attitude towards a given
	company
	\item Assembled portfolios for each subreddit based on their sentiment,
	and analyzed and compared the performance of these portfolios to
	determine a 'winner'
    \end{itemize}

    \vspace{3pt}
    \href{https://github.com/GabrieleMaurina/MoviePerformancePredictor}{\textbf{Movie
    Performance Predictor}}
    {\begin{itemize}[noitemsep,nolistsep]
	\item Used deep neural networks to determine the most imporatnt factor
	in movie success, both in terms of box office performance and
	critical/audience reviews
	\item Scraped data from websites including IMDB, RottenTomatoes, and
	BoxOfficeMojo, assembled data into a single coherent database for use in
	the project
    \end{itemize}}}
\vspace{8pt}
%-----------------------------------------------------------------------------------------------------------
%	Clearance
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Clearance}
    {Current TS/SSBI clearance, favorably adjudicated April 2019}
\vspace{8pt}

%-----------------------------------------------------------------------------------------------------------
%	Skills
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Skills}
    {\setstretch{1.25}
    \textbf{Python}: NumPy, pandas, PyTorch, OpenCV, Flask, Django, PySpark,
    pylint, pytest, Jupyer\\
    \textbf{Java:} Gradle, Groovy, JUnit, Cucumber\\
    \textbf{JavaScript:} TypeScript, React\\
    \textbf{Scripting:} Bash, Powershell\\
    \textbf{Big Data Tools:} SQL (PostgreSQL, MySQL, SQLite,
    SQLalchemy), Spark, Hadoop\\
    \textbf{Development Tools:} Linux (Debain/Ubuntu, Fedora/Red Hat, Unix),
    object-oriented programming, Containerization (Docker, Kubernetes), Git (GitHub, Bitbucket), AWS, CI/CD, Jenkins, Jira, Confluence}

\vspace{8pt}
%-----------------------------------------------------------------------------------------------------------
%	Education
%-----------------------------------------------------------------------------------------------------------
\resumesect
    {Education}
    {\textbf{Master's of Science - Computer Science} \hfill \normalsize{Jan. 2022 - Dec. 2025}\\
    Colorado State University \hfill \normalsize{Fort Collins, CO}\\
    \vspace{-6pt}\\
    \textbf{Bachelor's of Science - Computer Science} \hfill \normalsize{Jan. 2017 - May 2019}\\
    Metropolitan State University of Denver \hfill \normalsize{Denver, CO}}\\

\end{document}
